### 2025-06-02 ms.qmd
Update ms.qmd

>>>>

```{r, models_behaviour}
#| label: models_behaviour
#
refit <- FALSE
# A) L. delicata
deli_beh <- behav_clean %>% 
  filter(species == "delicata")
if(refit){
  deli_m_emergence <- brm(emergence ~ cort*temp*day + sex + (1 + day|lizard_id) + (1| clutch),
                        data = deli_beh,
                        family = bernoulli(link = "logit"),
                        chains = 4, cores = 4, iter = 4000, warmup = 1000,
                        control = list(adapt_delta = 0.99, max_treedepth =12))
  saveRDS(deli_m_emergence, file = here(#ADD FOLDER))
} else {
  deli_m_emergence <- readRDS(here(#ADD FOLDER))
}
summary(deli_m_emergence)
plot(deli_m_emergence)
```
